### 2014-03-14 docs/paper.tex
Some stuff on how stego is easier for us.

@@

@@

>>>>

\section{Introduction}

@@

\ldots

The fact that we tunnel inside HTTPS greatly eases the steganography problem.
It's not necessary to generate plausible HTTP, only plausible TLS.
TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
Of course, there are more subtle considerations that go into
making a circumvention HTTPS stream look like an allowed HTTPS stream,
things like packet size and timing, and duration of TCP connections.
These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.

@@

\section{Making the TLS handshake indistinguishable}
\label{sec:browserextension}

% Examples of how handshakes differ; e.g., OpenSSL versus NSS,
% and non-browser NSS versus browser NSS.

\section{Making traffic characteristics indistinguishable}
\label{sec:trafficstatistics}
